%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Methods\label{ch:methods}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Section comments: There were more changes related to objective language and directional words. There is a missing term near line 13.
The system identification of rigid body ship dynamics can be simplified into parameter estimation if parameterized physical models is assumed as the most appropriate model from a collection of candidate models.
The parameter estimations for roll motion and manoeuvring are presented in \autoref{sec:_roll} and \autoref{sec:_VMM}. The most appropriate models are selected in the model development process which is described in \autoref{sec:model_development_process}.

\section{Roll model parameter estimation} \label{sec:_roll}
\noindent Parameter estimation can be applied to identify the roll damping parameters ($B_1$, $B_2$, $B_3$) and stiffness parameters ($C_1$, $C_3$, $C_5$) in the parameterized roll motion models from the previous chapter (\autoref{eq:roll_decay_equation_himeno_linear}, \autoref{eq:roll_decay_equation_himeno_quadratic_b} and \autoref{eq:roll_decay_equation_cubic}). These equations do not have unique solutions because each equation can be multiplied by an arbitrary factor to obtain a new valid solution. Inertia is therefore excluded to obtain unique solutions. This is achieved by normalizing the equations by the total roll inertia $A_{44}$, as seen in \autoref{eq:roll_decay_nonedim_a44}, for the linear model.

\input{equations/roll_decay_nonedim_A44}

\noindent The identified normalized damping and stiffness parameters $B_{1A}$ and $C_{1A}$ can be expressed in dimensional units by multiplication with the normalization factor $A_{44}$. If $A_{44}$ is unknown before hand, it can be calculated using \autoref{eq:A_44_eq} \cite{piehl_ship_2016}, assuming that the meta center height $GM$ is known.
\input{equations/A_44_eq}

\noindent The frequency $\omega_0$ can be obtained with Fast Fourier transform (FFT) of the roll signal. 
Two methods for parameter estimation have been investigated: the ``derivation approach'', referred to in \textcite{imo_1200_2006}, and the ``integration approach'' used in \textcite{soder_assessment_2019} which are both described in the next subsections. 

\subsection{Derivation approach}\label{sec:derivation_approach}
In the derivation approach, \autoref{eq:roll_decay_nonedim_a44} is treated as a linear regression problem, where the states ($\phi$, $\dot{\phi}$, $\ddot{\phi}$) are known and the parameters $B_1$ and $C_1$ must be regressed. Only roll angle $\phi$ is known from the experimental data, which means that the velocity and acceleration $\dot{\phi}$, $\ddot{\phi}$ also must be estimated (note that this is done with numerical differentiation in Paper \ref{pap:rolldamping} and with the extended Kalman filter (EKF) in Paper \ref{pap:pit}).
A least squares fit must be applied to the roll motion equation to identify the damping and stiffness parameters.

\subsection{Integration approach}\label{sec:integration_approach}
In the integration approach, \autoref{eq:roll_decay_nonedim_a44} is solved as an ordinary differential equation (ODE) for many estimated sets of parameters until the solution converges. This method is time-consuming, and convergence is not guaranteed. However, the advantage is that only roll angle $\phi$ is needed.

\input{kappa/PIT}
\input{kappa/EKF}
\input{kappa/regression}
\input{kappa/generalization}
\input{kappa/model_development_process}
\input{kappa/VCT}

