%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Conclusions\label{ch:conclusions}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% The conclusions of the stated objectives...
% it was found that...
% it was shown that...
% it was proposed that...

%...short summary 
\noindent This thesis investigated the enhancement of ship manoeuvring models through the
integration of prior knowledge embedded in parametric model structures and semi-empirical
formulas together with additional VCT calculations. 
The main findings and conclusions are presented below, as well as the impacts of the work.

%Objective A,B
\subsection*{A parametric model structure and parameter identification technique for roll motion}
As demonstrated in Paper \ref{pap:rolldamping}, inverse dynamics regression (referred to as the derivation approach in that paper) is an efficient method for identifying parameters in parametric roll motion models. The study also showed that 250 roll decay tests were well described by the quadratic model structure. Consequently, this model structure was proposed as a robust framework for system identification of roll motion, offering good generalization.

%Objective C
\subsection*{Parameter identification techniques for ship manoeuvring models}
This thesis proposes parameter identification techniques for both FT and CT (VCT) data.

%C1
A new recursive inverse dynamics regression method for FT data, was proposed in Paper \ref{pap:pit}. This method combined inverse dynamics with an EKF in a two-step iterative approach \cite{yoonIdentificationHydrodynamicCoefficients2003}. The initial input model for this method was a linear maneuvering model with hydrodynamic derivatives estimated using semi-empirical formulas from the literature. The new method was found to be capable of effectively handling measurement noise and estimating the parameters within the models. 

%C2
A method was also proposed for CT data, with its novelty lying in the inclusion of the most critical states during maneuvers into the design of the VCT matrix. This consequently ensured coverage of the relevant regions of the state space. The method successfully identified a model for the Optiwise test case that showed strong agreement with the measured rudder forces and inverse dynamics forces for the FRMTs. This model also demonstrated good consistency with the corresponding closed-loop simulations. These results indicate that a physically accurate model with high prediction accuracy can be obtained using this proposed method, given accurate VCT data.  

% Objective D
\subsection*{Parametric model structure with good generalization identifiable from standard maneuvers}
% D1
It was found in Paper \ref{pap:pit} that a very complex manoeuvring model, such as the full Abkowitz model, could not be identified from standard manoeuvres where high multicollinearity was observed between the hydrodynamic derivatives. Model truncation was used to reduce the number of hydrodynamic derivatives to obtain more identifiable models while mitigating multicollinearity between the remaining hydrodynamic derivatives.

Model generalization from simpler to more complex maneuvers was assessed by identifying truncated models from zigzag tests to predict significantly different turning circle tests. The advance and tactical diameters were predicted within 5\% error for the two investigated ships. It was concluded that a truncated Abkowitz model identified from standard maneuvers is capable of satisfactorily simulating other standard maneuvers.

% D2
However, Paper \ref{pap:physics} showed that the truncated models in Paper \ref{pap:pit} did not generalize well when the ship was exposed to external wind forces. The model was found to be physically incorrect, despite being mathematically correct. The identification method failed to correctly separate the hull and rudder forces when only the total force of the inverse dynamics was available. A deterministic semi-empirical rudder model was proposed as a replacement for the data-driven rudder model to address this shortcoming. This steered the identification toward a more physically correct model with lower multicollinearity and better generalization to wind conditions, proving to be an effective mitigation strategy.

% D3
Despite these improvements, issues with multicollinearity persisted due to the high correlation between yaw rate and drift during standard maneuvers, preventing the identification of perfectly physically correct models in Paper \ref{pap:physics}. It was demonstrated that these problems could be resolved through additional VCT calculations to obtain more informative data, which proved to be an effective approach to mitigating this aspect of the multicollinearity, particularly in cases where CFD calculations are a viable and accurate option.

% Objective E
\subsection*{Semi-empirical formulas to improve generalization}
Several semi-empirical formulas available in the literature that incorporate prior hydrodynamic knowledge, potentially aiding model identification.       
Semi-empirical methods to predict roll damping were investigated in Paper \ref{pap:rolldamping}. Predictions with Ikeda's method, including 2D potential flow strip calculations, were in fair agreement with roll decay tests for 15 investigated ships. 
A more in-depth analysis of roll damping was conducted for the KVLCC2 test case in Paper \ref{pap:ikeda}. In this study, the 2D potential flow strip calculation was replaced by a more modern potential flow code. This combined approach produced roll motion predictions with high accuracy. It was thereby concluded that Ikeda's method provides a good semi-empirical method for predicting viscous roll damping.

Prior knowledge from semi-empirical formulas in the literature was used to estimate the initial input model for the recursive inverse dynamics regression method. This provided a reasonable prediction model of the EKF in the first iteration of this two-step method.

In Paper \ref{pap:physics}, a new semi-empirical rudder model was proposed for the twin rudder wPCC test case based on various semi-empirical formulas from the literature. The model was in good agreement with the VCT data in Paper \ref{pap:physics} and \ref{pap:vct}. 
A modified quadratic version of the MMG semi-empirical rudder model was proposed in Paper \ref{pap:vct}. 
It was shown that this model could satisfactorily predict the VCT data and the measured rudder forces during zigzag model tests for the single rudder Optiwise test case. 
The semi-empirical rudder model from Paper \ref{pap:physics} and the modified quadratic MMG rudder model from Paper \ref{pap:vct} belong to the same family of semi-empirical lifting-line rudder models, shown to be suitable for describing the true forces related to the rudder/rudders during standard manoeuvres. 

These examples have demonstrated that incorporating prior knowledge of ship hydrodynamics by using existing semi-empirical formulas from the literature can enhance the identification of ship dynamics models. This approach is particularly beneficial for data with insufficient persistence of excitation, leading to more physically accurate models with improved generalization. 

\subsection*{Impact of this work}
Throughout this research, inverse dynamics has proven to be a valuable tool for analyzing the forces acting on a ship during an FT. Comparing inverse dynamics forces with model force predictions provides a more informative assessment of model performance than through open-loop or closed-loop simulations. This approach ensures that the model and the experiment are always in the same state, which is not the case for simulations. From an engineering perspective, recalculating FT accelerations as forces is more convenient, especially when comparing them with forces from static VCT. Additionally, preprocessing FT data using inverse dynamics enables parameter identification in a manner similar to that of CT data.

This thesis has demonstrated that identifying a physically correct model with excellent generalization solely from standard manoeuvres FT data is challenging. The identification process may yield models that are mathematically correct but physically incorrect. These models may still predict other standard manoeuvres within a reasonable level of extrapolation. However, it has been shown that these models do not generalize well when wind forces are introduced.

Incorporating additional data from well-known semi-empirical models and VCT calculations improves the physical correctness and generalization of these models for applications requiring large extrapolations, such as those involving wind conditions. 