%!TEX root = ../main.tex
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Introduction}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The background of modelling SDTs with white-, black- or grey-box models is first introduced in this chapter followed by a brief literature review. The motivation and objective of this research is then stated followed by assumptions and limitations. The chapter ends with an outline of the whole thesis.

\section{Background}
Shipbuilding 4.0, at the principles of the Industry 4.0, will transform the design, manufacturing, operation, shipping, services, production systems, maintenance and value chains in all aspects of the shipbuilding 
industry \cite{stanic_toward_2018}.
The emergence of Internet-of-Things (IoT) has led to the introduction of the Internet-of-Ships (IoS) paradigm. \begin{quote} IoS is the interconnecting of sensing objects, such as ships, crews, cargoes, onboard equipments, waterway environment, waterway facilities, shore-based facilities, and other navigation elements, which are embedded with a variety of sensor and heterogeneous network technologies to enable these objects to collect and exchange data \cite{liu_internet_2016-1}.\end{quote}
Safety enhancements, route planning and optimization, energy efficiency, automatic berthing and autonomous shipping are some of the emerging applications for IoS \cite{aslam_internet_2020}.
A Ship Digital Twin (SDT) as a digital copy of a real ship, is one approach to achieve this \cite{chen_review_2021}. 
SDTs are data-driven in contrast to the related term Virtual Prototyping (VP), which is instead model based \cite{major_framework_2021}. A SDT is generally a model for an existing ship from where data can be collected and the VPs are generally prototypes for future ships, where no operational data is yet available.
In VP, white-box models are used. Either black-box or grey-box models are used in the SDTs. 

\begin{itemize}
    \item White-box modeling \\
    involves applying physical principles, so that no observed data is required, for instance Computational Fluid Dynamics (CFD). Semi-empirical models where unknown physical constants have been derived from historical experiments, can also be considered as white-box models \cite{leifsson_grey-box_2008}.  

    \item Black-box modeling \\
    means that parameters do not have physical significance but where the objectives is to find a good model that fits the observed data \cite{lindskog_tools_1995}.
    
    \item Grey-box modeling \\
    is a combination of white-box and black-box modeling methods, so that both a physical model and data is used. This concept is also referred as semi-physical modeling, hybrid modeling or semi-mechanistic modeling in the literature \cite{leifsson_grey-box_2008}. 
\end{itemize}

\noindent In a grey box model the white and black parts can be combined in several ways using either a serial or parallel approach \cite{leifsson_grey-box_2008} as seen in Fig.\ref{fig:greycombinations}. 

\begin{figure}[H]
    \centering
    \begin{subfigure}[b]{0.3\textwidth}
    \centering
    \begin{tikzpicture}[node distance=2cm]
    \node (white-box) [white-box] {White-box};
    \node (black-box) [black-box, right of=white-box, xshift=2cm] {Black-box};
    \draw [arrow] (white-box) -- (black-box);
    \end{tikzpicture}
    \caption{Serial grey-box}
    \label{fig:serial1}
    \end{subfigure}

    
    \begin{subfigure}[b]{0.3\textwidth}
    \centering
    \begin{tikzpicture}[node distance=2cm]
    \node (black-box) [black-box] {Black-box};
    \node (white-box) [white-box, right of=black-box, xshift=2cm] {White-box};
    \draw [arrow] (black-box) -- (white-box);
    \end{tikzpicture}
    \caption{Serial grey-box}
    \label{fig:serial2}
    \end{subfigure}

    \begin{subfigure}[b]{0.3\textwidth}
    \centering
    \begin{tikzpicture}[node distance=2cm]
    \node (black-box) [black-box] {Black-box};
    \node (white-box) [white-box, below of=black-box] {White-box};
    \node (join) [process, right of=black-box, xshift=2cm, yshift=-1cm] {join};
    \draw [arrow] (black-box) -- (join);
    \draw [arrow] (white-box) -- (join);
    \end{tikzpicture}
    \caption{Parallel grey-box}
    \label{fig:parallel}
    \end{subfigure}
    \caption{Several ways to combine white- and black-box models in grey box models.}
    \label{fig:greycombinations}
\end{figure}

\noindent The black-box modeling is entirely data driven, which means that no prior understanding of the system generating the data is needed and is therefore an attractive option for the SDT modelling. The black-box modeling may however give infeasible models outside the domain covered by the available data \cite{nielsen_machine_2022}. The white-box modeling does not have this problem, but does on the other hand require a full understanding of the system, which may be possible for special cases, but in general not possible for the complex scenario of a ship operating at sea. In the deep sea: wind, waves and current will add complexity. In coastal areas water depth and bank-effects will also add complexity \cite{nielsen_machine_2022}. 
\noindent Grey-box modelling is an attempt to bridge these problems, to either mitigate the white-box modelling error or the black-box extrapolation error.

Ship dynamics is a branch of ship hydrodynamics which concerns the ship forces and motions when the ship is allowed to move and rotate in all directions. Seakeeping and Manoeuvring are the two major sub fields, where Seakeeping studies the  behaviour of a ship in a seaway, under the influence of the external waves, currents and winds. Calm water conditions, lacking the external waves, are further assumed in Manoeuvring, which can either be thought of as an idealized simplification case of Seakeeping or actual conditions in sheltered environments. This thesis concerns rigid body ship dynamics in calm waters. The rigid body assumption simplifies the ship as a stiff body that does not transform under the act of forces. In this thesis, the rigid body ship dynamics is studied with the aim to develop better SDTs with grey-box modeling.

\section{Literature review}
SDT has a a positive trend in the number of publications during the recent years (2018-2021)  \cite{assani_ships_2022}. Most of the papers concerns ship equipment such as electric power systems, propulsion system, ship hull structure and marine diesel engines \cite{assani_ships_2022}. Only a minor part of the SDT applications handle ship trajectory, speed and fuel consumption \cite{assani_ships_2022}.   
Even though SDT is not explicitly mentioned, there are a lot of papers published about methods that can be used as SDTs. \cite{lang_comparison_2022} predicted the propulsion power for a chemical tanker for three test case voyages with high accuracy, using ML black-box modeling. The manoeuvres where however excluded. In another paper \cite{nielsen_machine_2022} used grey-box modelling for manoeuvring prediction of a ferry where a deep learning model (black-box) captures the residues between first-principles model (white-box) and observed data. These are very promising works that also show that there is still a lot to be done withing the field. 
A lot of research concerns the system identification of the ship's manoeuvring dynamics where a majority of the publications use simulated data as used in 
\cite{shi_identification_2009}, \cite{perera_system_2015}, \cite{zhu_parameter_2017} and \cite{wang_parameter_2021}. Some of the publications, for instance \cite{luo_parameter_2016} and \cite{he_nonparametric_2022} use data from physical model tests, where the measurement noise and the model uncertainty increases the complexity. 


%"Critic" to what has been done before
\section{Motivation and objective}
\label{sec:motivation}
% Motivation:
Huge amounts of data concerning ships' operation is collected daily around the oceans. We are still figuring out ways to make use of it. Models specialized in predicting specific aspects of the ship's operation, such as the fuel consumption, can be developed as black-box models with the latest technologies within Machine Learning (ML). It is in the author's belief that grey-box models, also incorporating physical relations, could give better prediction models to improve the SDTs. Introducing some aspects of ship dynamics into the model, gives a deeper understanding of the forces and motions of the ship, which can improve the accuracy of the SDTs to be used in the IoS applications. This approach will be explored in this thesis for the ship rigid body dynamics in calm waters.

Full scale operational data from ships at sea has a lot of noise and large uncertainties, due to the sea environment. Developing SDTs for this data is a great challenge. It is especially hard to know when the model is correct and when it is not. Instead, using data from a controlled laboratory environment, offers data from a similar environment, but with less noise and uncertainties. 
Model test data is therefore used in this thesis to develop SDT grey-box models of the ship rigid body dynamics. The hypothesis is that a SDT model that works in the lab, will also have potential to work at the sea. Or at least false models can be ruled out, since SDT models that do not work in the lab, will most likely not work at sea either. 

% Objective: 
\bigskip
\noindent Starting with reduced complexity and then gradually increasing the complexity has been a general approach to formulate the research objectives for this thesis:   


\subsubsection*{SDT for roll motion}
The first objective of the thesis is therefore to develop a SDT for the calm water ship rigid body dynamics in the roll degree of freedom, based on model test data.

\subsubsection*{SDT for manoeuvring}
The second objective is to increase the complexity by adding the surge, sway and yaw degrees of freedoms, addressing the manoeuvring problem.

\subsubsection*{SDT generalization}
The SDT must be able to make predictions outside the domain covered by the available data, in order to be of practical use in IoS applications. This addresses the generalization of the SDTs.

\section{Assumptions and limitations}
%Calm waters...
Calm water condition is a simplification of the real sea condition that a ship encounters. This condition assumes that the influences from encountering wind, waves and currents are neglected. These assumptions simplifies the system identification, by reducing the degrees of freedoms to: surge, sway, yaw and roll. Also note that all result are not necessarily directly transferable to full scale when model scale data is used, considering potential scale effects. 

\section{Outline of the thesis}
Chapter \ref{ch:models} presents the models for ship rigid body dynamics used in this thesis. The models for roll motion is introduced in Section \ref{sec:roll} and the manoeuvring motion models are introduced in Section \ref{sec:VMM}. These models represent the physical principles and thereby the white-box part of the developed grey-box models.
PITs, representing the black-box part, are used to regress the parameters of the white-box models. The PITs are introduced in Chapter \ref{ch:methods} for the roll motion and the manoeuvring motion in Section \ref{sec:PIT_roll} and Section \ref{sec:PIT_VMM}. 
A short summary of the appended papers, including research activities and a selection of the important results is presented in chapter \ref{ch:results}, followed by the conclusions in chapter \ref{ch:conclusions} and plans for future work in chapter \ref{ch:future_work}.

\input{kappa/models}
\input{kappa/methods}
\input{kappa/results}
\input{kappa/conclusions}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Future work\label{ch:future_work}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{New generic roll damping model}
The PIT of the roll motion models applied on 250 roll-decay tests that was investigated in Paper \ref{pap:rolldamping} produced a roll damping database for modern ship types. A grey-box model and a black-box model as described in Section \ref{sec:genericrolldampingmodel} was developed from this database. The prediction accuracy of these models were not very good and should be improved. This is important, especially since the SI method, being the state of art white-box physical model for roll damping, was found to be outside its limits for the ships in the database. This implies that there is a need for a new roll damping prediction method for modern ships.  