\subsection{Captive tests} \label{sec:CT}
Identifying a manoeuvring model from CMT or VCT is challenging: \say{All practical manoeuvring mathematical models are highly schematised and although in principle can be tuned to provide a satisfactory reproduction of the true motion, there are no simple theoretical methods for estimating their parameters} \cite{sutuloAlgorithmOfflineIdentification2014}.
\textcite{sutuloSynthesisExperimentalDesigns2004} developed a computer code for planning captive tests with D-optimized experimental designs so that the most precise estimates of model parameters could be obtained with the least number of experimental runs.
\textcite{sakamotoURANSSimulationsStatic2012} showed how added masses could be obtained from dynamic PMM simulations with unsteady Reynolds averaged Navier–Stokes (URANS) computations. \textcite{elmoctarRANSBasedSimulatedShip2014} used a similar approach to determine the added masses. 
However, \textcite{sakamotoURANSSimulationsStatic2012} strongly recommended using static tests for damping coefficients, instead of the single-run method applied on dynamic PMM tests.
\textcite{elmoctarRANSBasedSimulatedShip2014} identified an Abkowitz model from VCT for a twin-screw dock ship. Simulations with the VCT model were compared to CFD direct manoeuvring simulations and FRMT. Two different ways of modeling the propeller were investigated; the moving reference frame approach was 50 times faster than the sliding interface approach, but less accurate. The VCT model was found to be very efficient and results showed satisfactory agreement. However, the direct simulations showed better agreement.
\textcite{hajivandVirtualSimulationManeuvering2015} identified an Abkowitz model from VCT data for the DTMB 5512 model ship. The coefficients were determined from VCT data using a test program as outlined by \textcite{yoonBenchmarkCFDValidation2015c} that included oblique towing tests with drift angle variations at three speeds, and PMM tests of pure sway and pure yaw.
Simulations could not be compared with FRMT data since such tests were not available for the DTMB 5512 model ship. 
Instead, a comparison between simulations with models identified from VCT or captive model tests was conducted by \textcite{yoonBenchmarkCFDValidation2015c}; these were found to be in very good agreement.

\textcite{liuPredictionsShipManeuverability2018} identified an Abkowitz model from VCT data for the KCS container ship. Zigzag simulations with the identified model were compared with corresponding FRMT data \cite{simmanWorkshopVerificationValidation2014}. The simulations were also compared with previous simulations conducted by  \textcite{simonsenKCSPMMTests2014}  with a different model structure. This model structure was identified from both VCT and standard PMM model tests. The underprediction of zigzag overtshoot angles from all these simulations in relation to the FRMTs are summarized in \autoref{tab:liu2018}, where VCT A denotes the results from \textcite{liuPredictionsShipManeuverability2018} and VCT B and PMM B are the results from \textcite{simonsenKCSPMMTests2014} with the models obtained from either the VCT or PMM model tests.    
Since all values in this table are positive,t follows that all of the simulations underpredicted the FRMT overhoot angles. 
It would be reasonable to assume that the PMM model tests have the ability to provide a correct physical representation of the hydrodynamics in the FRMT. However, agreement between the PMM B simulations and the FRMT was not perfect. It seems that the accuracy of the model does not only depend on the accuracy of the CT data, but may also depend on which model structure is used and how the states are varied to identify the parameters.
\begin{table}[h]
    \centering
    \caption{Under predictions from the simulated overshoot angles (deg) in relation to FRMTs as reported in \textcite{liuPredictionsShipManeuverability2018}}
    \label{tab:liu2018}
    \pgfplotstabletypeset[col sep=comma, column type=c,
        columns/Overshoot/.style={column type=c,string type},
        %columns/Parameter/.style={column type=l,string type},
        %columns/Unit/.style={column type=l,string type,column name=~},
        %columns/Description/.style={column type=l,string type},
        %columns/Value/.style={column type=r, column name=~},
        every head row/.style={before row=\hline,after row=\hline},
        every last row/.style={after row=\hline}
    ]{tables/liu2018.csv}
\end{table}