% This page is hand-made. I could not make Biblatex to output the papers the way I wanted.

\begin{refsection}

This thesis is based on the following appended papers:

\begin{description}
% Biblatex \fullcite{Voronov2011} would work, but it uses maxcitenames, not maxbibnames, and there is no obvious way to change maxbibnames locally and change it back afterwards.
\item[Paper~\ref{pap:rolldamping}.]
\fullcite{alexandersson_analysis_2021}

\item[Paper~\ref{pap:motions}.] 
\fullcite{alexandersson_prediction_2021}

\item[Paper~\ref{pap:daiyong}.] 
\fullcite{alexandersson_comparison_2022}

\item[Paper~\ref{pap:pit}.] 
\fullcite{alexandersson_system_nodate}

\end{description}

\vspace{1cm}

\noindent Other relevant publications co-authored by Martin Alexandersson:
\begin{description}
\normalsize
\newcommand{\ME}{{\bfseries Alexey Voronov}}

\item Anna Tidstam, Lars-Ola Bligård, Fredrik Ekstedt, \ME, Knut Åkesson, Johan Malmqvist. \emph{Development of Industrial Visualization Tools for Validation of Vehicle Configuration Rules.} Proceedings of 9th International Symposium on Tools and Methods of Competitive Engineering, pp. 14, 2012.

\item Sajed Miremadi, \ME. \emph{Symbolic Reduction of Guards in Supervisory Control Using Genetic Algorithms.} Technical report. Göteborg: Chalmers University of Technology, 2012.

\item \ME, Knut Åkesson. \emph{Verification of Process Operations Using Model Checking.} Proceedings of IEEE International Conference on Automation Science and Engineering CASE'2009. pp. 415-420, 2009.

\item \ME, Knut Åkesson. \emph{Verification of Supervisory Control Properties of Finite Automata Extended with Variables.} Technical report. Göteborg: Chalmers University of Technology, 2009.

\item \ME, Knut Åkesson. \emph{Supervisory Control using Satisfiability Solvers.} Proceedings of 9th International Workshop on Discrete Event Systems WODES'2008, pp. 81-86, 2008.
\end{description}

\end{refsection}
